---
title: "Finding Fraudulent Job Postings: A First Look"
author: "Liam Edwards-Gaherty, Matthew Plisko, Andrew Polk, Henry Smith"
date: "4/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
#plotting and exploring
library(tidyverse) #for plotting and summarizing
library(GGally) #for nice scatterplot matrix 
library(ggridges) #for joy/ridge plots
library(corrplot) #for basic correlation matrix plot
library(naniar) #for exploring missing values
library(pdp) #for partial dependence plots, MARS models
library(rpart.plot) #for plotting decision trees
library(vip) #for importance plots
library(pROC) #for ROC curves
library(plotROC) #for plotting ROC curves

#making things look nice
library(lubridate) #for nice dates
library(knitr) #for nice tables
library(scales) #for nice labels on graphs
library(gridExtra) #for arranging plots
library(broom) #for nice model output
library(janitor) #for nice names

#data
library(ISLR) #for data
library(moderndive) #for data
library(rattle) #weather data
library(fivethirtyeight) #candy data

#modeling
library(rsample) #for splitting data
library(recipes) #for keeping track of transformations
library(caret) #for modeling
library(leaps) #for variable selection
library(glmnet) #for LASSO
library(earth) #for MARS models
library(rpart) #for decision trees
library(randomForest) #for bagging and random forests

theme_set(theme_minimal())
```

# Reading In The Data
```{r}
fake_job_postings <- read_csv("fake_job_postings.csv")
```

# Splitting the Data into Train and Test
```{r}
jobs <- fake_job_postings

#divide into training and testing
set.seed(253) #first set the seed!
jobs_split <- initial_split(jobs, prop = .7, 
                             strata = fraudulent)
jobs_train <- training(jobs_split)
jobs_test <- testing(jobs_split)

#distribution of response for the training data
table(jobs_train$fraudulent) %>% prop.table()

#distribution of response for testing data
table(jobs_test$fraudulent) %>% prop.table()

```


# Five Exploratory Plots/Tables

1. This plot explores the required_experience variable as it pertains to the fraudulent variable.
```{r}
jobs_train %>%
  ggplot(aes(x = as.factor(fraudulent), fill = required_experience)) +
  geom_bar() +
  scale_y_log10() +
  ggtitle("Fraudulent Versus Legitimate Job Postings, by Required Experience", subtitle = "Y Axis on Log Scale") +
  labs(x = "Fraudulent")
```

2. This plot explore the has_company_logo variable as it pertain to the fraudulent variable.
```{r}
jobs_train %>%
  ggplot(aes(x = as.factor(fraudulent))) +
  geom_bar(aes(fill = as.factor(has_company_logo))) +
  scale_y_log10() +
  ggtitle("Fraudulent Versus Legitimate Job Postings, by Inclusion of Company Logo", subtitle = "Y Axis on Log Scale") +
  labs(x = "Fraudulent", fill= "Has Company Logo")
```

3. This table shows that a job posting is overwhelmingly likely to be legitimate if it contains the company logo and has questions.
```{r}
jobs_train %>%
  filter(has_company_logo == 1, has_questions == 1) %>%
  count(fraudulent)
```


4. This plot filters for job location within the United States, showing that more than half of the job postings within the data are domestic.
```{r}
jobs_train %>%
  filter(str_detect(location, 'US')) %>%
  ggplot(aes(x = as.factor(fraudulent))) +
  geom_bar() +
  ggtitle("Fraudulent Versus Legitimate Job Postings, United States") +
  labs(x = "Fraudulent")
```

5. We think that delving deeper into the text input variables will help us create the best model. Below, we use the string detect function to filter by job postings that contain the word "must" in them, and the table shows the ratio of fraudulent postings, which remains consistent with the rest of the dataset.
```{r}
jobs_train %>%
  filter(str_detect(requirements, 'must')) %>%
  count(fraudulent)
```




# Research Questions
What are some universal signs of a fraudulent job posting?

What classification model best identifies the fraudulent job postings in the dataset? 

Can our model translate to detection of other fraudulent things like scam/spam email?

